%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   Context of the Project                   
%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Today mastering his domestic energy consumption is a major stake in our society. Everyear, bills related to energetic ressources increase, in 2013 French homes paid 3210\euro, an increase of more than 40\euro compared with 2012. And the ways set up to reduce them such as solar panels are still too expensive for the majority of the population and not enough effective during winter seasons.\\

In this context, the global objective of the project is to work on the design of a "box" called Smartee that can minimize the energy consumption of a building and maximize comfort. The Smart-Eco Box project was developed in a new growing market, known as Smart Energy Boxes.Although many sensors are already on the market, they are usually heterogeneous (for non-standardized ) which complicates their use in a system such as the one we would like to develop. Therefore members of the project will design a wireless communication system (box + associated sensors) for intelligent and efficient supervised management of energy consumption of a building from a website including the ability of the box to identify an electrical device in its ignition.\\

Once plugged in, the Smartee initialization detects sensors in the environment. Then a processing phase allows the box to work without any need for input by the client. This software allowed to detect bursts and initiated bursts processing received by a provided Universal Software Radio Peripheral (USRP). Finally data are stored in a database and energy consumption of the place is displayed on the website. 
